a and generators

### 2022-05-06 documentos/generators.tex
This is a basic implementation that works.
Comentarios resueltos

% \cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
% 
% 
% The symmetry for a PCE generator $\pceg$ is encoded in the 
% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
% is either symmetric or anti-symmetric under reflection of the 
% indices in the $k$-th position in $\vec\alpha$. 
% Consider the map
% \begin{equation}
% % \Sigma: 
% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
% \label{eq:Sigma}
% \end{equation}
% Indeed, any generator is a subspace containing half the elements of the full vector space.  
% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
% \begin{enumerate}
% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
% \end{enumerate}
% From the first property, we now obtain
% \begin{equation}
% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
% \end{equation}
% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
%

@@

>>>>

% 
% 
% The symmetry for a PCE generator $\pceg$ is encoded in the 
% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
% is either symmetric or anti-symmetric under reflection of the 
% indices in the $k$-th position in $\vec\alpha$. 
% Consider the map
% \begin{equation}
% % \Sigma: 
% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
% \label{eq:Sigma}
% \end{equation}
% Indeed, any generator is a subspace containing half the elements of the full vector space.  
% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
% \begin{enumerate}
% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
% \end{enumerate}
% From the first property, we now obtain
% \begin{equation}
% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
% \end{equation}
% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
%

@@

\cpnote{The connection between rows or columns of $a$ and single-qubit PCE
generators is shown, with the 1s identified with preserved components and
the $-1$s with deleted ones. For any number of particles, such simple relation 
still holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}. }
\janote{The connection between rows or columns of $a$ and single-qubit PCE
generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
left with the sets $\{\tau_\alpha\}$ of preserved and erased components
by each $\mathcal G_\alpha$.
For any number of particles, such simple relation 
holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
